Turbulence in compact to giant H~II regions

### 2023-04-23 strucfunc_paper.tex
Improve the marking of changes
Define a macro \NEW to do it and use a red that is not so
garish. Also, make sure that spacing works right around section
headers, etc. And turn off link colorization to simplify things.

% Use more muted colors for links
\hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
  urlcolor=blue!50!black}

@@

@@

\definecolor{WillCommentColor}{rgb}{0.6,0.11,0.4}
\newcommand\WILL[1]{\textbf{\color{WillCommentColor}#1}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Two observational effects can modify the observed structure function at the smallest scales.
The first is the blurring of the observed image by atmospheric seeing,
which tends to reduce \(B(r)\) for small \(r\).
In Appendix~\ref{sec:effects-seeing-struc}, we perform numerical experiments
with synthetic velocity fields and find that
a good approximation to the effects of seeing is to multiply
the model structure function by a factor:
\begin{equation}\label{eq:ffs}
  \color{red}
  S(r) =
  \left[ \frac{1}{1 + 1.25 s_0 / r_0} \right]
  \left[ \frac{1}{1 + (2.6 s_0 / r)^{1.5}} \right]
  ,
  %  S(r) = \frac{
  %   e^{-s_0 / r_0}
  % }{
  %   1+(2s_0 / r)^{2 / 3}
  % } ,
\end{equation}
where \(s_0\) is the RMS width of the seeing profile\footnote{%
  Note that the full-width half maximum (FWHM) seeing width is
  \(2 (2 \ln 2)^{1/2} s_0 \approx 2.35 s_0\).
},
and \(r_0\) is the correlation length.
An example is shown by the green line in Figure~\ref{fig:model-strucfunc}a.
The effect of seeing is to make the structure function 
bend down away from the idealized power law, 
becoming increasingly steep at scales smaller than \(s_0\),
but having a noticeable effect at scales up to \(10 \times s_0\).

@@

\appendix
\colorlet{RED}{red}
\section{\color{red}Degradation of the structure function due to observational limitations}
\label{sec:degr-struct-funct}
% Studied in context of \(\Delta\)-variance by \citet{Bensch:2001l}.

To characterize the impact of the finite map size
and the atmospheric seeing on the structure function we perform a series of experiments using artificial turbulent velocity maps.
We quantify how these observational limitations affect the determination of
the structure function parameters, such as
the correlation length \(r_0\) and the velocity field variance \(\sigma\pos^2\). 
The synthetic velocity maps are created using a modified version of the \textcolor{red}{\texttt{make\textunderscore{}3dfield}} command from the \texttt{turbustat} Python library \citep{Koch2019AJ....158....1K},
which creates a \textcolor{red}{three-dimensional} fractional Brownian Motion field
\citep{Miville-Deschenes:2003a}
based on a power-law energy spectrum in wavenumber \(k\), \(E(k) \propto k^{-n}\),
where \textcolor{red}{\(n = m + 3\)} and with random phases. 
Our modification multiplies the energy spectrum by a
low-wavenumber exponential taper:
\(e^{-1 / 2 \pi r_0 k}\).
As a result, the generated fields become uncorrelated at scales larger than \(r_0\)
and the resulting structure function closely approximates our model form
(section~\ref{sec:methods-apply}).

{\color{red}%
  In order to create 2D plane-of-sky velocity map, we first
  create 3D cubes of fluctuating velocity and emissivity
  with \texttt{make\textunderscore{}3dfield},
  then transform to a PPV (position-position velocity) cube
  using the \texttt{make\textunderscore{}ppv} command from \texttt{turbustat},
  assuming thermal broadening with FWHM of \SI{20}{\kilo\meter\per\second},
  as appropriate for a hydrogen line at \(T \approx \SI{e4}{K}\).
  Finally, the first velocity moment map is obtained
  by integrating along the velocity axis.

  For the emissivity field, we assume a log-normal distribution
  with RMS fractional width
  \(\shortsig{E} = 1.0\) that is typical of our sources
  (see footnote~\ref{fn:brightness-fluctuations} and Figure~\ref{fig:brightness-pdfs} above).
  We further assume that there is no correlation between the emissivity
  and velocity fluctuations and that their spatial correlation length
  and power law indices are equal.\footnote{%
    We have investigated departures from these assumptions and found that they
    make very little difference to the results.
  }
}

@@

\subsection{\color{red}Finite box effects}
\label{sec:finite-box-effects}

@@

\begin{figure}
  \begin{tabular}{@{} l @{}}
    (a)\\ \includegraphics[width=0.95\linewidth]{Figures/fake-3d-finite-box-effect-ems-fluct_sigE_1}
    \\[\bigskipamount]
    (b)\\ \includegraphics[width=0.95\linewidth]{Figures/fake-finite-box-fits-ems-fluct_sigE_1}
  \end{tabular}
  \caption{
    Reduction of apparent velocity variance and correlation length
    due to finite box size.
    (a)~Empirical measurements of \(\sigma^2\) and \(r_0\).
    Colored dots show mean results from different simulated velocity fields,
    with different power law slopes.
    Colored shading shows the inter-quartile range over the different sub-images.
    The dashed line is an approximate analytic fit to these results
    (\(\color{red}1 - e^{L / 4.0r_0}\)).
    (b)~Determination of \(\sigma^2\) and \(r_0\) from fitting the model
    of equation~\eqref{eq:new-correlation-form}.
    Colored dots are mean results from different simulated velocity fields,
    while the dashed line is the same as in (a).
  }
  \label{fig:finite-box-effect}
\end{figure}

\textcolor{red}{Figure~\ref{fig:finite-box}a} shows how we test for finite map effects by taking
a simulated \textcolor{red}{1st moment map of} size \(512 \times 512\) pixels and iteratively
dividing the full map into \(2 \times 2\) tiles.
On the \(j\)th iteration we have \(N = 4^j\) tiles,
each of size \(L \times L \) pixels with \(L = 2^{9 - j}\).
The figure shows the result for \(j = 1\), 2, 3, and 4, in which the full map
was generated with a correlation length \textcolor{red}{\(r_0 = 32\)~pixels}.
We then calculate the individual structure function for each tile and
find the mean and standard deviation for each level of subdivision,
showing the results in \textcolor{red}{Figure~\ref{fig:finite-box}b}.
It can be seen that the mean structure functions for each level
of subdivision (shown by colored dots and solid lines)
overlap very closely with one another, apart from deviations
due to edge effects when \(r > L/2\).
On the other hand, there is considerable dispersion between
individual tiles (shown by light colored shading) for the cases
where \(L < r_0\).

We next empirically measure the velocity variance and
apparent correlation length for each tile.
The velocity variance \(\sigma^2\) is found by
directly averaging over the pixels in the tile using equation~\eqref{eq:sig-pos},
while the apparent correlation length \(r_0\)
is found as the separation \(r\) for which \(B(r) = \sigma^2\),
using the tile's own empirically measured structure function and variance.
In \textcolor{red}{Figure~\ref{fig:finite-box-effect}a} we show how these
quantities deviate from the ``true'' values
(as measured on the full \(512 \times 512\) map)
as a function of the tile size \(L\).
It can be seen that the true values are successfully recovered
so long as the map size is more than ten times the correlation length,
but the apparent values of \(r_0\) and \(\sigma^2\) are smaller than the true values
when \(L < 10 r_0\), increasingly so as \(L\) becomes smaller.
This can be intuitively understood as due to the fact that a tile that
is small compared with the correlation length will
fail to sample the full range of velocity fluctuations,
leading to an underestimate of \(\sigma^2\).
Then the fact that \(B(r)\) increases with \(r\) in the power law regime
means there will be a concomitant underestimate of \(r_0\).

However, it is possible to do a considerably better job
of recovering the true \(\sigma^2\) and \(r_0\) by fitting our
heuristic model structure function of equation~\eqref{eq:model-strucfunc-ideal}.
This is shown in \textcolor{red}{Figure~\ref{fig:finite-box-effect}b}, where it can be seen
that the true parameters are reliably recovered so long as \textcolor{red}{\(L > 5 r_0\)},
which is a roughly \SI{0.5}{dex} improvement over the purely empirical method.
In order for the model fitting to work, the tile size must be large enough
that the structure function begins to show some flattening at the largest scales,
which is why the results are still inaccurate for the smallest values of \(L\)
that sample only the rising power-law portion of \(B(r)\).

\subsection{\color{red}Effects of seeing}
\label{sec:effects-seeing-struc}

\begin{figure}
  \begin{tabular}{@{} l @{}}
    (a)\\
    \includegraphics[width=\linewidth]{Figures/fake-3d-seeing-nonp-ems-fluct-thumbnails_sigE_1}\\
    (b)\\
    \includegraphics[width=\linewidth]{Figures/fake-seeing-nonp-3d-ems-fluc_m4-reduction_sigE_1}
  \end{tabular}
  \caption{Effects of seeing on the structure function.
    (a)~Each row shows a different simulated random velocity field
    on a \(256^2\) grid (see text for details).
    The left column shows the original field,
    while the remaining columns show the effects of smoothing by a gaussian kernel
    with RMS width \(s_0\) from 1 to 32 pixels.
    The same color scale is used for all columns, ranging from \(-3\) to \(+3\) times
    the standard deviation of the unsmoothed map.
    (b)~Relative change in the second-order structure function due to the gaussian smoothing.
    Solid lines with symbols show the average over the 4 maps of
    \(B(r, s_0) / B(r, s_0 = 0)\) as a function of separation \(r\),
    with a separation of \textcolor{red}{\(2.6 s_0\)} indicated by a large filled circle on each curve.
    Dashed lines shows the empirical fit discussed in the text.
    The dotted line shows the correlation length of the original fields,
    while colored plus symbols show the apparent correlation length of the smoothed fields.
  }
  \label{fig:seeing-reduction}
\end{figure}

@@

\textcolor{red}{Figure~\ref{fig:seeing-reduction}a} illustrates how four different
synthetic \textcolor{red}{1st-moment maps of} size \(256\times256\) pixels
and correlation length \textcolor{red}{\(r_0 = \SI{32}{pixels}\)}
are affected by progressively broader gaussian seeing,
with RMS width \(s_0 = 1\) to \SI{32}{pixels}.
\textcolor{red}{%
  Note that the seeing is applied to each velocity channel of the
  PPV emissivity cube before integrating to find the 2D velocity map.
}
We calculate the structure function \(B(r)\) for each map and show
in Figure~\ref{fig:seeing-reduction}b the average ratio between
\(B(r)\) and the value in the absence of seeing,
with different colors representing different values of \(s_0\).
Results are shown for a power-law slope of \textcolor{red}{\(m = 1.0\)}
but we find very similar behaviour for other values of \(m\) within the range
seen in our observations.
For small values of \(s_0\), the principle effect is seen at
the smallest separations but the structure function is noticeably depressed
for separations as large as \(r = 10 s_0\).
As \(s_0\) increases to become comparable with \(r_0\),
even the largest separations are significantly affected.
At the same time the apparent correlation length begins to increase,
as indicated by the plus symbols in the figure.

We find that the following simple analytic function reproduces
these results to within better than 10\%:
%\begin{equation}\label{eq:seeingemp2}
%S(r; s_0, r_0) = \frac{e^{-s_0 / r_0}}{1+(2s_0 / r)^{2a}} ,
%\end{equation}
\begin{equation}\label{eq:seeingemp2}\color{red}
S(r; s_0, r_0) = 
  \left [
\left (1+a_1\frac{s_0}{r_0} \right) 
\left(1+ \left (a_2 \frac{ s_0}{r} \right) ^{a_3} \right)
  \right ]^{-1} ,
\end{equation}
which is shown by dashed lines in \textcolor{red}{Figure \ref{fig:seeing-reduction}b}.
\textcolor{red}{%
  The exact values of the constants \(a_1\), \(a_2\), \(a_3\)
  are found to depend slightly on the power law slope \(m\)
  and the magnitude of the emissivity fluctuations \(\shortsig{E}\).
  We adopt the compromise values \(a_1 = 1.25\),
  \(a_2 = 2.6\), and \(a_3 = 1.5\), which fit the numerical results to
  within 20\% for \(0.8 < m < 1.2\) and \(0.5 < \shortsig{E} < 2.0\).}
The optimum value of the index \(a\) in this equation varies slightly
with the power law slope \(m\) of the true structure function,
but a compromise value of \(a = 0.75\) works tolerably well for \(m = 0.7\) to \(1.3\).
We therefore use this equation to represent the seeing
in our structure function fits (section~\ref{sec:results}),
with \(s_0\) as an additional free parameter for the models.
\clearpage

@@

@@

More recent measurements of the structure function of the Lagoon Nebula
have used the [\ion{O}{3}] \Wav{5007} line and have probed smaller scales.
\citep{1987ApJ...317..676O} used longslit observations at a small number of position angles
to study the structure function over an area \(\num{2} \times \SI{2}{arcmin^2}\),
centered on the nebula's principal ionizing star, 9~Sgr.
However, it is hard to compare their results to ours, as they carry out
a Gaussian decomposition of the line profile into two components, A and B,
and analyse the structure function of the two components separately.
The total variance of component A (the stronger and narrower of the two)
is \SI{2}{km^{2}.s^{-2}} at scales \(< \SI{1}{pc}\),
which is significantly smaller than our value of \SI{7}{km^{2}.s^{-2}},
but this is not surprising since they are probing scales smaller than the
correlation length and therefore suffer from a severe finite-box effect.
Component~B on the other hand shows a much larger variance
of \SI{13}{km^{2}.s^{-2}} and an essentially flat structure function.

@@

>>>>

% Use more muted colors for links
% \hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
%   urlcolor=blue!50!black}
\hypersetup{hidelinks=True}

@@

% Mark new changes in red
\definecolor{NEWcolor}{rgb}{0.7,0.2,0.1}
\newcommand\startNEW{\color{NEWcolor}}
\newcommand\stopNEW{\color{black}}
\newcommand\NEW[1]{\startNEW #1\stopNEW\relax}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Two observational effects can modify the observed structure function at the smallest scales.
The first is the blurring of the observed image by atmospheric seeing,
which tends to reduce \(B(r)\) for small \(r\).
In Appendix~\ref{sec:effects-seeing-struc}, we perform numerical experiments
with synthetic velocity fields and find that
a good approximation to the effects of seeing is to multiply
the model structure function by a factor:
\begin{equation}\label{eq:ffs}
  \startNEW
  S(r) =
  \left[ \frac{1}{1 + 1.25 s_0 / r_0} \right]
  \left[ \frac{1}{1 + (2.6 s_0 / r)^{1.5}} \right]
  ,
  \stopNEW
\end{equation}
where \(s_0\) is the RMS width of the seeing profile\footnote{%
  Note that the full-width half maximum (FWHM) seeing width is
  \(2 (2 \ln 2)^{1/2} s_0 \approx 2.35 s_0\).
},
and \(r_0\) is the correlation length.
An example is shown by the green line in Figure~\ref{fig:model-strucfunc}a.
The effect of seeing is to make the structure function 
bend down away from the idealized power law, 
becoming increasingly steep at scales smaller than \(s_0\),
but having a noticeable effect at scales up to \(10 \times s_0\).

@@

\appendix
\colorlet{RED}{red}
\startNEW
\section{Degradation of the structure function due to observational limitations}
\label{sec:degr-struct-funct}
\stopNEW
% Studied in context of \(\Delta\)-variance by \citet{Bensch:2001l}.

To characterize the impact of the finite map size
and the atmospheric seeing on the structure function we perform a series of experiments using artificial turbulent velocity maps.
We quantify how these observational limitations affect the determination of
the structure function parameters, such as
the correlation length \(r_0\) and the velocity field variance \(\sigma\pos^2\). 
The synthetic velocity maps are created using a modified version of the \NEW{\texttt{make\textunderscore{}3dfield}} command from the \texttt{turbustat} Python library \citep{Koch2019AJ....158....1K},
which creates a \NEW{three-dimensional} fractional Brownian Motion field
\citep{Miville-Deschenes:2003a}
based on a power-law energy spectrum in wavenumber \(k\), \(E(k) \propto k^{-n}\),
where \NEW{\(n = m + 3\)} and with random phases. 
Our modification multiplies the energy spectrum by a
low-wavenumber exponential taper:
\(e^{-1 / 2 \pi r_0 k}\).
As a result, the generated fields become uncorrelated at scales larger than \(r_0\)
and the resulting structure function closely approximates our model form
(section~\ref{sec:methods-apply}).

\startNEW
In order to create a 2D plane-of-sky velocity map, we first
create 3D cubes of fluctuating velocity and emissivity
with \texttt{make\textunderscore{}3dfield},
then transform to a PPV (position-position velocity) cube
using the \texttt{make\textunderscore{}ppv} command from \texttt{turbustat},
assuming thermal broadening with FWHM of \SI{20}{\kilo\meter\per\second},
as appropriate for a hydrogen line at \(T \approx \SI{e4}{K}\).
Finally, the first velocity moment map is obtained
by integrating along the velocity axis.

For the emissivity field, we assume a log-normal distribution
with RMS fractional width
\(\shortsig{E} = 1.0\) that is typical of our sources
(see footnote~\ref{fn:brightness-fluctuations} and Figure~\ref{fig:brightness-pdfs} above).
We further assume that there is no correlation between the emissivity
and velocity fluctuations and that their spatial correlation length
and power law indices are equal.\footnote{%
  We have investigated departures from these assumptions and found that they
  make very little difference to the results.
}
\stopNEW

@@

\startNEW
\subsection{Finite box effects}
\label{sec:finite-box-effects}
\stopNEW

@@

\begin{figure}
  \begin{tabular}{@{} l @{}}
    (a)\\ \includegraphics[width=0.95\linewidth]{Figures/fake-3d-finite-box-effect-ems-fluct_sigE_1}
    \\[\bigskipamount]
    (b)\\ \includegraphics[width=0.95\linewidth]{Figures/fake-finite-box-fits-ems-fluct_sigE_1}
  \end{tabular}
  \caption{
    Reduction of apparent velocity variance and correlation length
    due to finite box size.
    (a)~Empirical measurements of \(\sigma^2\) and \(r_0\).
    Colored dots show mean results from different simulated velocity fields,
    with different power law slopes.
    Colored shading shows the inter-quartile range over the different sub-images.
    The dashed line is an approximate analytic fit to these results
    (\NEW{\(1 - e^{L / 4.0r_0}\)}).
    (b)~Determination of \(\sigma^2\) and \(r_0\) from fitting the model
    of equation~\eqref{eq:new-correlation-form}.
    Colored dots are mean results from different simulated velocity fields,
    while the dashed line is the same as in (a).
  }
  \label{fig:finite-box-effect}
\end{figure}

\NEW{Figure~\ref{fig:finite-box}a} shows how we test for finite map effects by taking
a simulated \NEW{1st moment map of} size \(512 \times 512\) pixels and iteratively
dividing the full map into \(2 \times 2\) tiles.
On the \(j\)th iteration we have \(N = 4^j\) tiles,
each of size \(L \times L \) pixels with \(L = 2^{9 - j}\).
The figure shows the result for \(j = 1\), 2, 3, and 4, in which the full map
was generated with a correlation length \NEW{\(r_0 = 32\)~pixels}.
We then calculate the individual structure function for each tile and
find the mean and standard deviation for each level of subdivision,
showing the results in \NEW{Figure~\ref{fig:finite-box}b}.
It can be seen that the mean structure functions for each level
of subdivision (shown by colored dots and solid lines)
overlap very closely with one another, apart from deviations
due to edge effects when \(r > L/2\).
On the other hand, there is considerable dispersion between
individual tiles (shown by light colored shading) for the cases
where \(L < r_0\).

We next empirically measure the velocity variance and
apparent correlation length for each tile.
The velocity variance \(\sigma^2\) is found by
directly averaging over the pixels in the tile using equation~\eqref{eq:sig-pos},
while the apparent correlation length \(r_0\)
is found as the separation \(r\) for which \(B(r) = \sigma^2\),
using the tile's own empirically measured structure function and variance.
In \NEW{Figure~\ref{fig:finite-box-effect}a} we show how these
quantities deviate from the ``true'' values
(as measured on the full \(512 \times 512\) map)
as a function of the tile size \(L\).
It can be seen that the true values are successfully recovered
so long as the map size is more than ten times the correlation length,
but the apparent values of \(r_0\) and \(\sigma^2\) are smaller than the true values
when \(L < 10 r_0\), increasingly so as \(L\) becomes smaller.
This can be intuitively understood as due to the fact that a tile that
is small compared with the correlation length will
fail to sample the full range of velocity fluctuations,
leading to an underestimate of \(\sigma^2\).
Then the fact that \(B(r)\) increases with \(r\) in the power law regime
means there will be a concomitant underestimate of \(r_0\).

However, it is possible to do a considerably better job
of recovering the true \(\sigma^2\) and \(r_0\) by fitting our
heuristic model structure function of equation~\eqref{eq:model-strucfunc-ideal}.
This is shown in \NEW{Figure~\ref{fig:finite-box-effect}b}, where it can be seen
that the true parameters are reliably recovered so long as \NEW{\(L > 5 r_0\)},
which is a roughly \SI{0.5}{dex} improvement over the purely empirical method.
In order for the model fitting to work, the tile size must be large enough
that the structure function begins to show some flattening at the largest scales,
which is why the results are still inaccurate for the smallest values of \(L\)
that sample only the rising power-law portion of \(B(r)\).

\startNEW
\subsection{Effects of seeing}
\label{sec:effects-seeing-struc}
\stopNEW

\begin{figure}
  \begin{tabular}{@{} l @{}}
    (a)\\
    \includegraphics[width=\linewidth]{Figures/fake-3d-seeing-nonp-ems-fluct-thumbnails_sigE_1}\\
    (b)\\
    \includegraphics[width=\linewidth]{Figures/fake-seeing-nonp-3d-ems-fluc_m4-reduction_sigE_1}
  \end{tabular}
  \caption{Effects of seeing on the structure function.
    (a)~Each row shows a different simulated random velocity field
    on a \(256^2\) grid (see text for details).
    The left column shows the original field,
    while the remaining columns show the effects of smoothing by a gaussian kernel
    with RMS width \(s_0\) from 1 to 32 pixels.
    The same color scale is used for all columns, ranging from \(-3\) to \(+3\) times
    the standard deviation of the unsmoothed map.
    (b)~Relative change in the second-order structure function due to the gaussian smoothing.
    Solid lines with symbols show the average over the 4 maps of
    \(B(r, s_0) / B(r, s_0 = 0)\) as a function of separation \(r\),
    with a separation of \NEW{\(2.6 s_0\)} indicated by a large filled circle on each curve.
    Dashed lines shows the empirical fit discussed in the text.
    The dotted line shows the correlation length of the original fields,
    while colored plus symbols show the apparent correlation length of the smoothed fields.
  }
  \label{fig:seeing-reduction}
\end{figure}

@@

\NEW{Figure~\ref{fig:seeing-reduction}a} illustrates how four different
synthetic \NEW{1st-moment maps of} size \(256\times256\) pixels
and correlation length \NEW{\(r_0 = \SI{32}{pixels}\)}
are affected by progressively broader gaussian seeing,
with RMS width \(s_0 = 1\) to \SI{32}{pixels}.
\NEW{%
  Note that the seeing is applied to each velocity channel of the
  PPV emissivity cube before integrating to find the 2D velocity map.
}
We calculate the structure function \(B(r)\) for each map and show
in Figure~\ref{fig:seeing-reduction}b the average ratio between
\(B(r)\) and the value in the absence of seeing,
with different colors representing different values of \(s_0\).
Results are shown for a power-law slope of \NEW{\(m = 1.0\)}
but we find very similar behaviour for other values of \(m\) within the range
seen in our observations.
For small values of \(s_0\), the principle effect is seen at
the smallest separations but the structure function is noticeably depressed
for separations as large as \(r = 10 s_0\).
As \(s_0\) increases to become comparable with \(r_0\),
even the largest separations are significantly affected.
At the same time the apparent correlation length begins to increase,
as indicated by the plus symbols in the figure.

We find that the following simple analytic function reproduces
these results to within better than 10\%:
%\begin{equation}\label{eq:seeingemp2}
%S(r; s_0, r_0) = \frac{e^{-s_0 / r_0}}{1+(2s_0 / r)^{2a}} ,
%\end{equation}
\begin{equation}\label{eq:seeingemp2}
  \startNEW
  S(r; s_0, r_0) = 
  \left [
    \left (1+a_1\frac{s_0}{r_0} \right) 
    \left(1+ \left (a_2 \frac{ s_0}{r} \right) ^{a_3} \right)
  \right ]^{-1} ,
  \stopNEW
\end{equation}
which is shown by dashed lines in \NEW{Figure \ref{fig:seeing-reduction}b}.
\NEW{%
  The exact values of the constants \(a_1\), \(a_2\), \(a_3\)
  are found to depend slightly on the power law slope \(m\)
  and the magnitude of the emissivity fluctuations \(\shortsig{E}\).
  We adopt the compromise values \(a_1 = 1.25\),
  \(a_2 = 2.6\), and \(a_3 = 1.5\), which fit the numerical results to
  within 20\% for \(0.8 < m < 1.2\) and \(0.5 < \shortsig{E} < 2.0\).}
The optimum value of the index \(a\) in this equation varies slightly
with the power law slope \(m\) of the true structure function,
but a compromise value of \(a = 0.75\) works tolerably well for \(m = 0.7\) to \(1.3\).
We therefore use this equation to represent the seeing
in our structure function fits (section~\ref{sec:results}),
with \(s_0\) as an additional free parameter for the models.
\clearpage

@@

% START of revised material
\startNEW

@@

More recent measurements of the structure function of the Lagoon Nebula
have used the [\ion{O}{3}] \Wav{5007} line and have probed smaller scales.
\citet{1987ApJ...317..676O} used longslit observations at a small number of position angles
to study the structure function over an area \(\num{2} \times \SI{2}{arcmin^2}\),
centered on the nebula's principal ionizing star, 9~Sgr.
However, it is hard to compare their results to ours, as they carry out
a Gaussian decomposition of the line profile into two components, A and B,
and analyse the structure function of the two components separately.
The total variance of component A (the stronger and narrower of the two)
is \SI{2}{km^{2}.s^{-2}} at scales \(< \SI{1}{pc}\),
which is significantly smaller than our value of \SI{7}{km^{2}.s^{-2}},
but this is not surprising since they are probing scales smaller than the
correlation length and therefore suffer from a severe finite-box effect.
Component~B on the other hand shows a much larger variance
of \SI{13}{km^{2}.s^{-2}} and an essentially flat structure function.

@@

% END of revised material
\stopNEW
